---
title: "GenomeDB_Exploring_GTEx"
author: "Nick Burns"
date: "5 October 2016"
output: html_document
---

# GenomeDB: exploring GTEx  

Have finally got GenomeDB reloaded, with dbSNP147 as the reference coordinate system. GTEx data is in there, and I just want to make sure that the data looks really similar to GenomeDB-version1. This will be a basic, cheery picked exploration of a few gene regions to make sure that everything looks roughly correct.  

## Preparation  

Create a connection to the database, and setup the query template and the visualisation template

```{r}
library(RODBC)
library(data.table)
library(ggplot2)

conn <- odbcConnect("R-SQL")
sqlQuery(conn, "use GenomeDB")

query <- "
    select
    	G.gene_symbol, T.smtsd, S.chromosome, S.position, Q.pvalue
    from fact_qtl Q
      inner join dim_gene G on G.gene_id = Q .gene
      inner join dim_tissue T on T.tissue_id = Q.tissue
      inner join dim_snp S on S.snp_id = Q.snp
    where G.gene_symbol = '%s'
      and T.smts = '%s'"

display <- function (qtls) {
    ggplot(qtls, aes(x = position / 1000000, y = -log10(pvalue))) +
        geom_point(colour = "darkblue", alpha = 0.5) +
        theme_minimal() +
        xlab("position (mb)") +
        ylab("-log10( pvalue )") 
}
```

## Quick visualisations

ABCG2:

```{r}
abcg2 <- sqlQuery(conn, sprintf(query, "ABCG2", "Thyroid"))
head(abcg2)

display(abcg2)
```

FTO:
```{r}
qtl <- sqlQuery(conn, sprintf(query, "FTO", "Blood"))
head(qtl)

display(qtl)
```

IRX3:
```{r}
qtl <- sqlQuery(conn, sprintf(query, "IRX3", "Pancreas"))
head(qtl)

display(qtl)
```

PPARG:
```{r}
qtl <- sqlQuery(conn, sprintf(query, "PPARG", "Brain"))
head(qtl)

display(qtl)
```

TCFL7:

```{r}
qtl <- sqlQuery(conn, sprintf(query, "TCF7L2", "Blood Vessel"))
head(qtl)

display(qtl)
```

ACSL5
```{r}
qtl <- sqlQuery(conn, sprintf(query, "ACSL5", "Blood"))
head(qtl)

display(qtl)
```


This is great news! Everything looks really sensible, and consistent with the visualisations from Version 1 of GenomeDB.


## Close db connection

```{r}
odbcClose(conn)
```