---
title: "GTEx_DataPreparation"
author: "Nick Burns"
date: "23 September 2016"
output: html_document
---

## GTEx Data Wrangling  

There are a few little tidy up things that I need to do with the GTEx data:  

  1. Standardise the metadata (specifically, the SMTSD names) so that these can be matched  
  
```{r}
setwd("G:/Datasets/GenomeDBData/")
library(data.table)

meta_data <- fread("gtex_metadata.csv")
meta_data
```

What I really want to do here is strip out any non-alpha characters from the SMTSD column so that it matches the naming convention used in the QTL files.

```{r}
clean_smtsd <- function (x, target) {
    gsub(target, "", x)
}
targets <- c("- ", "\\(", "\\)")
for (target in targets) {
    meta_data[, SMTSD := clean_smtsd(SMTSD, target)]
}

meta_data[1:100, SMTSD]
```

That worked nicely. There are also some blank SMTS rows. In all cases, these are redundant and so I will move them entirely

```{r}
meta_data <- meta_data[nchar(SMTS) > 3]
```

Finally, write this file back to disk

```{r}
write.csv(meta_data, "gtex_metadata.csv", row.names = FALSE, quote = FALSE)
```